CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-12-18 codecheck-paper.tex
add HDSR to todo list
codecheck can help enforce journal policies

\begin{itemize}
\item Check with Giuliano re: ``code works''. Write to Naomi.
\item Use "execution" insteand of "sharing" in title?
\item Can we introduce "research compendium" as a term?
\item Should we make code and data sharing a prerequisite or leave that door open?
\item Take a look at the Lancet's statistical review process (areas for improvement by authors) \url{https://www.thelancet.com/journals/lancet/article/PII0140-6736(92)90409-V/fulltext}
\item How to relate to "reproducibility does not matter but trust does", see \url{https://gmbecker.github.io/MayInstituteKeynote2019/outline.html}
\item Should we ask the people currently listed in the acknowledgements?
\item revisit \url{https://github.com/codecheckers/discussion}
\end{itemize}

@@

\textbf{Step 3:} the CODECHECKER runs the code, based on instructions provided by
the author, and checks if some/all of the results from the paper can be
reproduced. (See later for exact nature of ``reproduced''). If there are
any problems running the code, the CODECHECKER asks the author for help
to resolve the problems. The burden to provide reproducible material lies with
the author.
The CODECHECKER then tries to run the code again.
This process iterates until either the CODECHECKER is successful,
or the CODECHECKER concludes the code does not work (\emph{what do in this
case}). As part of this process, the CODECHECKER could work entirely
locally on their own compute resource, or in the cloud, e.g.~using the open
MyBinder infrastructure \cite{jupyter_binder_2018} or alternatives, some of which
are more tailored for scientific publications while others offer commercial
options to, e.g., publishers (cf. \cite{konkol_publishing_2020}).
Using such cloud-based 
infrastructure allows for the CODECHECKER and author to collaboratively improve
the code and enforces a much more complete definition of the computing environment,
but, unless infrastructure is provided by, e.g., by the publisher, requires code
and data to be published openly online.
Note that the taks of the CODECHECKER is to check the ``mechanics'' of the
workflow, not to evaluate its correctness. 
Stodden et~al. \cite{stodden_setting_2013} destinguish between verification and
validation in the context of Mathematics, and in the same vein a CODECHECK
ensures a verification\footnote{Note this is a different use as the \emph{Verification Reports} article type in the journal \emph{Cortex}
\cite{chambers_verification_2020}},
i.e., checking that the code correctly produces the 
output it claims to create, but not a validation, i.e., does the code implement
the right algorithm to solve the problem that is researched, 
of the computational results.

>>>>

\begin{itemize}
\item Check with Giuliano re: ``code works''. Write to Naomi.
\item Use "execution" insteand of "sharing" in title?
\item Can we introduce "research compendium" as a term?
\item Should we make code and data sharing a prerequisite or leave that door open?
\item Take a look at the Lancet's statistical review process (areas for improvement by authors) \url{https://www.thelancet.com/journals/lancet/article/PII0140-6736(92)90409-V/fulltext}
\item How to relate to "reproducibility does not matter but trust does", see \url{https://gmbecker.github.io/MayInstituteKeynote2019/outline.html}
\item Should we ask the people currently listed in the acknowledgements?
\item revisit \url{https://github.com/codecheckers/discussion}
\item \url{https://hdsr.mitpress.mit.edu/pub/f0obb31j/release/1} and other articles form the HDSR special issue
\end{itemize}

@@

\textbf{Step 3:} the CODECHECKER runs the code, based on instructions provided by
the author, and checks if some/all of the results from the paper can be
reproduced. (See later for exact nature of ``reproduced''). If there are
any problems running the code, the CODECHECKER asks the author for help
to resolve the problems. The burden to provide reproducible material lies with
the author.
The CODECHECKER then tries to run the code again.
This process iterates until either the CODECHECKER is successful,
or the CODECHECKER concludes the code does not work (\emph{what do in this
case}). As part of this process, the CODECHECKER could work entirely
locally on their own compute resource, or in the cloud, e.g.~using the open
MyBinder infrastructure \cite{jupyter_binder_2018} or alternatives, some of which
are more tailored for scientific publications while others offer commercial
options to, e.g., publishers (cf. \cite{konkol_publishing_2020}).
Using such cloud-based 
infrastructure allows for the CODECHECKER and author to collaboratively improve
the code and enforces a much more complete definition of the computing environment,
but, unless infrastructure is provided by, e.g., by the publisher, requires code
and data to be published openly online.
Note that the taks of the CODECHECKER is to check the ``mechanics'' of the
workflow, not to evaluate its correctness. 
Stodden et~al. \cite{stodden_setting_2013} destinguish between verification and
validation in the context of Mathematics, and in the same vein a CODECHECK
ensures a verification\footnote{Note this is a different use as the \emph{Verification Reports} article type in the journal \emph{Cortex}
\cite{chambers_verification_2020}},
i.e., checking that the code correctly produces the 
output it claims to create, but not a validation, i.e., does the code implement
the right algorithm to solve the problem that is researched, 
of the computational results.
Nevertheless, the simple attempt to reproduce may highlight shortcomings in
a submission with respect to transparency as it may be required by a journal's
policy and help to resolve misunderstandings and discrepancies
(cf.~\cite{christian_journal_2020}).
